Project Thesis/Report

### 2022-01-01 Gandhi_Project_Report/draft1.tex
Done 4.4

The next result is of relative import but to fully comprehend its influence, some discussion still remains. Before stating it, we define a concept which will directly be shown to be equivalent to the USP.

\begin{Definition}
  [\bf Uniform Attraction Property]\label{Dfn_UAP}
  A driven system $g$ has the Uniform Attraction Property (UAP) if, regardless of starting position, all trajectories converge to a single trajectory as time flows forward. 
  This trajectory is also the unique solution sequence $x$ to the input sequence $u$ as mentioned above \ref{here_UAP_firstestablished}.
\end{Definition}

\begin{Theorem}
  The following statements are equivalent:
  \vspace{-8mm}
  \begin{enumerate}[noitemsep, label=\roman*.]
    \item $g$ has the USP 
    \item $g$ is a topological contraction 
    \item $g$ has the Unique Attraction Property (UAP). 
  \end{enumerate}
\end{Theorem}
\begin{proof}
  (we’ll show this)  [11] eqn.6 
\end{proof}

We have not as of yet treated the UAP properly, and establish the necessary result here (without proof) so as not to break up the completeness of theorem.

\textbf{The proof of the result for the UAP is left to literature. Why? Cite.}

@@

We make special note of a specific driven system. The function

\begin{equation}  \label{eqn_driveng}
%    \[ 
g(u,x)=(1-a)x+a{\cdot}tanh(Au+\alpha{a}Bx)
% \]
\end{equation}

is both SI-invertible and possesses the USP. The proof of these two facts is rather involved and  hence the proof, instead of being replicated here, may be found in (cite relevant article) 
This specific driving function $g$ is used in our implementation and is more completely discussed in chapter \ref{sect5}

\textbf{Expand: UAP + Embedding $\rightarrow$  perturbation isn’t an issue + we can drop left-infinite sequence.  }

Despite the ease that one may work with a left-infinite history in the realm of theory, it is impossible to obtain such a sequence in any real-life application.  
One does not in practice, fortunately, need the entire left-infinite history of the input thanks to the Uniform Attraction Property (UAP). 
The next definition is stated in an informal manner as the more rigourous definition makes use of processes, a concept which would take some amount of paper to establish and prove - an exercise which would detract from the principal thrust of this paper/project/thesis.

@@

Recall that the Unique Attraction Property guarantees that all trajectories \textit{(which ones?)} will converge to the same trajectory in forward time. 
Incredibly, this permits one to initialise a driven system $g$ with an altogether arbitrary initial value $y_m\in{X}$ where $m\in\mathbb{Z}$ and the UAP guarantees that the sequence $\{y_{m+1}, y_{m+2},\ldots\}$ satisfying the relation $y_n=g(u_n, y_{n-1})$  where $k\geq{m}$  will uniformly approach the elements $\{x_n\}$ of the actual solution. (see [41, Theorem 1] or [11, Eqn. (18)])

@@

\begin{figure}[ht]
  \includegraphics[scale=0.4]{memloss_conttime.png}
  \centering
  \label{fig:memoryLosscont_time}
%\caption{Approaching the true solution if g has the UAP}
\end{figure}

One may now appreciate an even more astounding result. $g$ having the USP is equivalent to the UAP and so one need not establish any additional results to ensure that the sequence uniformly approach the unique solution $\Psi$. This vastly simplifies the work needed to be done in setting up a problem to guarantee that the underlying system will be accurately 'represented' by the conjugate system. \textbf{Check this statement again to make sure it's not nonsensical.}

This also solves the problem of perturbations or noise introduced by the observable or measurement function. \textbf{(rephrase, expand and explain)}

@@

The following theorem establishes the existence of a well-defined map GT describing the single-delay dynamics of the system above.

@@

Note that $H_2$ maps an entire left-infinite solution sequence from $\Psi$ to an element in $X\times{X}$.

We now have the following (compare with \ref{SCausal_H} above):

\emph{graph here causes issues currently}
% \begin{center}
% %    \[ 
%       \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
%       \everypsbox{\scriptstyle}
%       \begin{psmatrix}
%       \widehat{U}_T  && \widehat{U}_T \\
%       Y_T && Y_T \\
%       %%%
%      %  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{h}
%      %  \ncline{1,2}{2,2} > {H_2}
%      %  \ncline{2,1}{2,2}^{G_T}
%       \end{psmatrix}
%      % \]
%     \end{center}

\textbf{Show that $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$. }

\textbf{Summarising the discussing thus far:}
It is easy to lose onself in the symbols, so we take a moment to review our progress up until this point.

\vspace{-8mm}
\begin{enumerate}
\item We are interested in a dynamical system $(U,T)$ with unknown dynamics for whichever reason.
\item To determine information about this system $(U,T)$, we shift our focus by rather aiming to determining the dynamics of the inverse-limit system $(\widehat{U}, \widehat{T})$ which, given certain assumptions, we can guarantee to be at least semi-conjugate to $(U,T)$.
\item If the driven system $g$ (and $\{u_n\}$ in $U$  is an orbit of $T$), we have that $G_T$ exists. 
\item If, furthermore, $g$ may be shown to have the USP, we showed that $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
\item If $T$ is also (and at this stage this is very much our hope) a homeomorphism, then $(Y_T, G_T)$ topologically conjugate to $(\widehat{U}, \widehat{T})$ in which $(U,T)$ has been embedded! 
\end{enumerate} 
One can therefore learn the single-delay lag dynamics of the driven system states via $G_T$ with enough data thanks to the USP. This enables us to do at least 2 things: 1) Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined. 2) Forecast future values of $u_n$.

@@

By establishing the existence of the map $G_T$, we’ve essentially embedded the attractor $U$ \textbf{So far we haven't really spoken about an attractor} into the higher dimensional space $X\times{X}$.
In layman’s terms, this ensures that there is more “dimensional room” for the underlying system’s underlying dynamics to “move”. As the dynamics aren’t as “squashed”, we might therefore hope that the dynamics of $G_T$ are in some sense simpler than that of $T$. (Taken note of the fact that $G_T$ is a homeomorphism even when $T$ is just continuous)

>>>>

The next result is of relative import but to fully comprehend its influence, some discussion still remains. We state it in part and postpone the proof.
% Before stating it, we define a concept which will directly be shown to be equivalent to the USP.

\begin{Theorem}
  The following statements are equivalent:
  \vspace{-8mm}
  \begin{enumerate}[noitemsep, label=\roman*.]
    \item $g$ has the USP. 
    \item $g$ is a topological contraction.
  \end{enumerate}
\end{Theorem}
\begin{proof}
  (postponed)  [11] eqn.6 
\end{proof}

% We have not as of yet treated the UAP properly, and establish the necessary result here (without proof) so as not to break up the completeness of theorem.

% \textbf{The proof of the result for the UAP is left to literature. Why? Cite.}

@@

We make special note of a specific driven system. The function 
\begin{equation}  \label{eqn_driving}
g(u,x)=(1-a)x+a{\cdot}tanh(Au+\alpha{a}Bx)
\end{equation} 
is both SI-invertible and possesses the USP. The proof of these two facts is rather involved and  hence the proof, instead of being replicated here, may be found in \textbf{(cite relevant article)}
This specific driving function $g$ is used in our implementation and is more completely discussed in chapter \ref{sect5}

Despite the ease that one may work with a left-infinite history in the realm of theory, it is impossible to obtain such a sequence in any real-life application.  
One does not in practice, fortunately, need the entire left-infinite history of the input thanks to the Uniform Attraction Property (UAP).

\begin{Definition}
  [\bf Uniform Attraction Property]\label{Dfn_UAP}
  A driven system $g$ has the Uniform Attraction Property (UAP) if, regardless of starting position, all trajectories \textbf{(of what?)} converge to a single trajectory as time flows forward. 
  This trajectory is also the unique solution sequence $x$ to the input sequence $u$ as mentioned above \ref{here_UAP_firstestablished}.
\end{Definition}

This definition is stated in a not completely rigourous manner as the more formal definition makes use of processes, a concept which would take some time to establish and detracts from the principal thrust of this paper/project/thesis.

@@

As the Unique Attraction Property guarantees that all trajectories \textit{(which ones?)} will converge to the same trajectory as time moves forward. 
Incredibly, this permits one to initialise a driven system $g$ with an altogether arbitrary initial value $y_m\in{X}$ where $m\in\mathbb{Z}$ and the UAP then guarantees that the sequence $\{y_{m+1}, y_{m+2},\ldots\}$ which satisfies the relation $y_n=g(u_n, y_{n-1})$  for  $k\geq{m}$  will uniformly approach the elements $\{x_n\}$ of the actual solution. (see [41, Theorem 1] or [11, Eqn. (18)])

@@

\begin{figure}[ht]
  \includegraphics[scale=0.4]{memloss_conttime.png}
  \centering
  \label{fig:memoryLosscont_time}
\caption{Approaching the true solution if g has the UAP}
\end{figure}

One may now appreciate an even more astounding result: $g$ having the USP is equivalent to the UAP. We restate the above theorem.

\begin{Theorem}
  The following statements are equivalent:
  \vspace{-8mm}
  \begin{enumerate}[noitemsep, label=\roman*.]
    \item $g$ has the USP.
    \item $g$ is a topological contraction.
    \item $g$ has the UAP.
  \end{enumerate}
\end{Theorem}
\begin{proof}
  (We'll show this)  [11] eqn.6 
\end{proof}

One need therefore not establish any additional results to ensure that the sequence uniformly approaches the unique solution $\Psi$. This vastly simplifies the effort necessary to set up a problem in order to guarantee that the underlying system will be accurately represented by the conjugate system.

This also solves the problem of perturbation/noise introduced by the observable or measurement function. Recall from before that an observable is inherently a map that discretises the underlying continuous-time system. Moreover, measurement and device error introduce mistakes. Since we are working with a chaotic system displaying sensitive dependence on initial conditions, these small errors could potentially send the trajectory into a completely different attractor. In the presence of the UAP, however, small measurement errors introduced into the system do not pose the same danger as before.

\textbf{(Rephrase and/or expand)}

@@

The following theorem establishes the existence of a well-defined map $G_T$ describing the single-delay dynamics of the system above.

@@

Note that $H_2$ maps an entire left-infinite solution sequence from $\Psi$ to an element in $X\times{X}$.
We now have the following (compare with \ref{SCausal_H} above):

\begin{equation}
  %  \[ 
      \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
      \everypsbox{\scriptstyle}
      \begin{psmatrix}
      \widehat{U}_T  && \widehat{U}_T \\
      Y_T && Y_T \\
      %%%
     %  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{h}
     %  \ncline{1,2}{2,2} > {H_2}
     %  \ncline{2,1}{2,2}^{G_T}
      \end{psmatrix}
    %  \]
    \end{equation}

\begin{Theorem}
    $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
\end{Theorem}
\begin{proof}
  \textbf{Show}
\end{proof}

\subsubsection*{Summarising the discussing thus far:}

It is easy to lose the birds-eye view, so we take a moment to review our progress up until this point.

\vspace{-8mm}
\begin{enumerate}
\item We are interested in a some dynamical system $(U,T)$ with unknown dynamics.
\item To determine properties about this system $(U,T)$ and predict its future evolution, we determine the dynamics of the inverse-limit system $(\widehat{U}, \widehat{T})$. Given certain assumptions, we can guarantee that $(\widehat{U}, \widehat{T})$ is at least semi-conjugate to $(U,T)$.
\item If the driven system $g$ is SI-invertible (and $\{u_n\}\in{U}$  is an orbit of $T$), the map $G_T$ exists. 
\item If, furthermore, $g$ has the USP, $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
\item If we can assume that $T$ is a homeomorphism, $(Y_T, G_T)$ is topologically conjugate to $(\widehat{U}, \widehat{T})$, an extension space of $(U,T)$
\end{enumerate}

One can therefore learn the single-delay lag dynamics of the driven system states via $G_T$ with enough data thanks to the USP/UAP. This enables us to do at least 2 things: 
\vspace{-8mm}
\begin{itemize}
\item Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined.
\item Forecast future values of $u_n$. 
\end{itemize}

@@

By establishing the existence of the map $G_T$, we’ve essentially embedded the attractor $U$ \textbf{(So far we haven't really spoken about an attractor)} into the higher dimensional space $X\times{X}$. \textbf{(Why is it true that it's higher-dimensional?)}
In layman’s terms, this ensures that there is more “dimensional room” for the underlying system’s underlying dynamics to “move”. As the dynamics aren’t as “squashed”, we might therefore hope that the dynamics of $G_T$ are in some sense simpler than that of $T$. (Taken note of the fact that $G_T$ is a homeomorphism even when $T$ is just continuous)
